The Talking Heads Experiment

### 2015-04-27 chap5/chap5.tex
fixed remaining typos

We need to find an architecture by which 
an agent can establish the relation between form and meaning, 
in other words verbalise a meaning to produce an utterance
and parse an utterance to retrieve its meaning. This 
mechanism needs to be flexible enough to deal with the 
unavoidable synonymy and amiguity that will arise. 
Second, we need to find a mechanism by which an agent 
can acquire and help construct the lexicon 
of the group. 
A shared lexicon should emerge
through the distributed activities of the agents without any prior
design or global co-ordination. Third, the lexicon formation 
process should scale up to handle a growing and ever
changing set of meanings and continue to work even with 
large populations whose constitution changes in time. 
It should be possible for new agents to enter the population
and acquire the existing language and for agents to 
leave without destabilising the whole system. These
are formidable challenges, particularly because we 
want to find the simplest possible solution, something 
a one year old child could do without fully 
developed intelligence.

@@

\begin{table}
\begin{center}
\begin{tabular}{ l  l }
\lsptoprule
{\itshape meaning} & {\itshape form} \\ 
\midrule{}
{}[\textsc{dark}] & coba \\ 
{}[\textsc{large}] & wabidu \\ 
... & ... \\ 
\lspbottomrule
\end{tabular}
\end{center}
\caption{\label{tab:t-mem}Associative memory of a single agent.}
\end{table}
As an agent is acquiring his lexicon, there are going to 
be stages when he is not yet sure about the meaning of 
a certain form. So it must be possible for the agent
to store different 
meanings for the same form and different forms for the
same meaning. This can easily be done by extending the memory capacity
to cross-associate multiple items. Agents can then 
handle amiguity (one word can have different
meanings) and synonymy (one meaning can 
be associated with many different words).

@@

The operations of speaker and hearer are summarised in 
\figref{incr-decr} assuming that speaker and hearer
use both the score table above (in reality they of 
course always have different score tables). 
The speaker collects all possible
forms for a given meaning [\textsc{dark}], chooses the one with the
highest score (`pama'), and transmits that form. 
The hearer collects all possible meanings for 
the transmitted form ([\textsc{dark}], [\textsc{large}]) and again chooses the one with
the highest score. If the hearer's meaning is equal to that
of the speaker's, the game succeeds. The score of 
two used associations increases and the others
decrease, implementing lateral 
inhibition. If the game fails, only the two used associations 
go down.\footnote{More or less neural realism can be introduced to 
model this associative memory. In our experiments we 
have a perfectly working memory that can store an 
association as soon as it has seen it once. This makes
theoretical investigation easier and makes it possible
to better follow the simulations and experimentations.  
An example of a neural network solution to lexical
memory is discussed in \cite{Cangelosi:1996}.}

@@

In the next game shown below, the speaker is 
{\bfshape a4}, the hearer {\bfshape a5} and the topic
{}[\textsc{small}]. Now the speaker is successful in creating a word, namely 
`di'. The hearer receives the word, does not know it,
but stores it in association with [\textsc{small}]. The game still fails. 
\begin{verbatim}
Game 29
   a4 is the speaker. a5 is the hearer. 
   a4 categorises the topic as [SMALL]
   a4 creates a new word: di
   a5 does not know di
   a4 points to the topic
   a5 categorises the topic as [SMALL]
   a5 stores di as [SMALL]
\end{verbatim}
In game 32, something similar happens. This time {\bfshape a5} creates
a new word `pida' for [\textsc{large}]. {\bfshape a3} does not know 
the word but stores it. 
\begin{verbatim}
Game 32
   a5 is the speaker. a3 is the hearer. 
   a5 categorises the topic as [LARGE]
   a5 creates a new word: `pida'
   a5 says: pida
   a3 does not know pida
   a5 points to the topic
   a3 categorises the topic as [LARGE]
   a3 stores pida as [LARGE]
\end{verbatim}
A first success occurs in game 43, when {\bfshape a5} uses again 
`pida' for [\textsc{large}]. {\bfshape a3} hears `pida', has associated it 
in his lexicon with [\textsc{large}], and so the game succeeds. 
\begin{verbatim}
Game 43
   a5 is the speaker. a3 is the hearer. 
   a5 categorises the topic as [LARGE]
   a5 says: pida
   a3 interprets pida as [LARGE]
   a3 points to the topic 
   a5 signals OK
\end{verbatim}
It is quite tedious to go through such games by hand. 
For large populations of agents or meanings, even the 
most diligent researcher soon loses patience. Fortunately 
it is not so difficult to implement the Naming Game model on 
a computer. This makes large-scale simulations, even with 
hundreds of agents and meanings feasable, and ensures
that they have been done correctly.
All traces and graphs of games reported in this book
have been produced by computer simulations or physical 
experiments with the Talking Heads.

@@

The lexicons of individual agents contain quite a few form-meaning
pairs that did not make it in the shared lexicon that gradually 
emerged. It is entirely feasable to envision a pruning mechanism 
that would eliminate from memory those form-meaning pairs whose 
success has been non-existent (for example because an agent created
it as speaker but it was never picked up by anybody else), 
or whose score has become zero (because another word became
dominant). The impact of such a forgetting
function has not been explored yet in our experiments.

@@

Self-organisation is not unique to biological phenomena,\is{increasing returns economics}
on the contrary, similar situations have been intensively
studied in economics, where
the complex adaptive systems paradigm has recently also 
lead to many interesting new insights, as discussed in \cite{Arthur:1996}. 
For certain types of products, particularly in 
information technology where the cost of manufacturing 
and distribution is negligable compared to the cost
of design, a winner-take-all situation can be observed. 
One product, for example a particular operating system or 
a particular microprocessor, comes to dominate the market.

@@

The analogies between self-organisation 
in language and other fields is important for three reasons. 
First of all, if self-organisation is ubiquitous in nature
and has succesfully explained so many phenomena, its incorporation
into a model of language becomes independently motivated, and
therefore the explanatory force of the model increases. 
What is new and different is that the principle is applied
to a non-material self-organising entity, but nevertheless
the same sort of dynamics can be seen.

@@

However, this general evolution hides the more interesting
developments. \figref{figure-coherence-in-space}
shows the evolution of coherence for each
cluster (a, b, c) separately and
also for the total set of agents. As long as the agents
have relatively little contact, total coherence is low
although the lexical coherence within each cluster is high. 
Total coherence starts to increase with increased contact. Coherence in
each cluster diminishes somewhat because the agents in the
cluster are in the process of accomodating to the global lexicon. 
This means that the
languages of the different groups are in the process of
merging due to the increased language contact.

>>>>

We need to find an architecture by which 
an agent can establish the relation between form and meaning, 
in other words verbalise a meaning to produce an utterance
and parse an utterance to retrieve its meaning. This 
mechanism needs to be flexible enough to deal with the 
unavoidable synonymy and ambiguity that will arise. 
Second, we need to find a mechanism by which an agent 
can acquire and help construct the lexicon 
of the group. 
A shared lexicon should emerge
through the distributed activities of the agents without any prior
design or global co-ordination. Third, the lexicon formation 
process should scale up to handle a growing and ever
changing set of meanings and continue to work even with 
large populations whose constitution changes in time. 
It should be possible for new agents to enter the population
and acquire the existing language and for agents to 
leave without destabilising the whole system. These
are formidable challenges, particularly because we 
want to find the simplest possible solution, something 
a one year old child could do without fully 
developed intelligence.

@@

\begin{table}
\begin{center}
\begin{tabular}{ l  l }
\lsptoprule
{\itshape meaning} & {\itshape form} \\ 
\midrule{}
{}[\textsc{dark}] & coba \\ 
{}[\textsc{large}] & wabidu \\ 
... & ... \\ 
\lspbottomrule
\end{tabular}
\end{center}
\caption{\label{tab:t-mem}Associative memory of a single agent.}
\end{table}
As an agent is acquiring his lexicon, there are going to 
be stages when he is not yet sure about the meaning of 
a certain form. So it must be possible for the agent
to store different 
meanings for the same form and different forms for the
same meaning. This can easily be done by extending the memory capacity
to cross-associate multiple items. Agents can then 
handle ambiguity (one word can have different
meanings) and synonymy (one meaning can 
be associated with many different words).

@@

The operations of speaker and hearer are summarised in 
\figref{incr-decr} assuming that speaker and hearer
use both the score table above (in reality they of 
course always have different score tables). 
The speaker collects all possible
forms for a given meaning [\textsc{dark}], chooses the one with the
highest score (`pama'), and transmits that form. 
The hearer collects all possible meanings for 
the transmitted form ([\textsc{dark}], [\textsc{large}]) and again chooses the one with
the highest score. If the hearer's meaning is equal to that
of the speaker's, the game succeeds. The score of 
two used associations increases and the others
decrease, implementing lateral 
inhibition. If the game fails, only the two used associations 
go down.\footnote{More or less neural realism can be introduced to 
model this associative memory. In our experiments we 
have a perfectly working memory that can store an 
association as soon as it has seen it once. This makes
theoretical investigation easier and makes it possible
to better follow the simulations and experiments.  
An example of a neural network solution to lexical
memory is discussed in \cite{Cangelosi:1996}.}

@@

In the next game shown below, the speaker is 
{\bfshape a4}, the hearer {\bfshape a5} and the topic
{}[\textsc{small}]. Now the speaker is successful in creating a word, namely 
`di'. The hearer receives the word, does not know it,
but stores it in association with [\textsc{small}]. The game still fails. 
\begin{verbatim}
Game 29
   a4 is the speaker. a5 is the hearer. 
   a4 categorises the topic as [SMALL]
   a4 creates a new word: di
   a5 does not know di
   a4 points to the topic
   a5 categorises the topic as [SMALL]
   a5 stores di as [SMALL]
\end{verbatim}
In game 32, something similar happens. This time {\bfshape a5} creates
a new word `pida' for [\textsc{large}]. {\bfshape a3} does not know 
the word but stores it. 
\begin{verbatim}
Game 32
   a5 is the speaker. a3 is the hearer. 
   a5 categorises the topic as [LARGE]
   a5 creates a new word: `pida'
   a5 says: pida
   a3 does not know pida
   a5 points to the topic
   a3 categorises the topic as [LARGE]
   a3 stores pida as [LARGE]
\end{verbatim}
A first success occurs in game 43, when {\bfshape a5} uses again 
`pida' for [\textsc{large}]. {\bfshape a3} hears `pida', has associated it 
in his lexicon with [\textsc{large}], and so the game succeeds. 
\begin{verbatim}
Game 43
   a5 is the speaker. a3 is the hearer. 
   a5 categorises the topic as [LARGE]
   a5 says: pida
   a3 interprets pida as [LARGE]
   a3 points to the topic 
   a5 signals OK
\end{verbatim}
It is quite tedious to go through such games by hand. 
For large populations of agents or meanings, even the 
most diligent researcher soon loses patience. Fortunately 
it is not so difficult to implement the Naming Game model on 
a computer. This makes large-scale simulations, even with 
hundreds of agents and meanings feasible, and ensures
that they have been done correctly.
All traces and graphs of games reported in this book
have been produced by computer simulations or physical 
experiments with the Talking Heads.

@@

The lexicons of individual agents contain quite a few form-meaning
pairs that did not make it in the shared lexicon that gradually 
emerged. It is entirely feasible to envision a pruning mechanism 
that would eliminate from memory those form-meaning pairs whose 
success has been non-existent (for example because an agent created
it as speaker but it was never picked up by anybody else), 
or whose score has become zero (because another word became
dominant). The impact of such a forgetting
function has not been explored yet in our experiments.

@@

Self-organisation is not unique to biological phenomena,\is{increasing returns economics}
on the contrary, similar situations have been intensively
studied in economics, where
the complex adaptive systems paradigm has recently also 
lead to many interesting new insights, as discussed in \cite{Arthur:1996}. 
For certain types of products, particularly in 
information technology where the cost of manufacturing 
and distribution is neglectible compared to the cost
of design, a winner-take-all situation can be observed. 
One product, for example a particular operating system or 
a particular microprocessor, comes to dominate the market.

@@

The analogies between self-organisation 
in language and other fields is important for three reasons. 
First of all, if self-organisation is ubiquitous in nature
and has successfully explained so many phenomena, its incorporation
into a model of language becomes independently motivated, and
therefore the explanatory force of the model increases. 
What is new and different is that the principle is applied
to a non-material self-organising entity, but nevertheless
the same sort of dynamics can be seen.

@@

However, this general evolution hides the more interesting
developments. \figref{figure-coherence-in-space}
shows the evolution of coherence for each
cluster (a, b, c) separately and
also for the total set of agents. As long as the agents
have relatively little contact, total coherence is low
although the lexical coherence within each cluster is high. 
Total coherence starts to increase with increased contact. Coherence in
each cluster diminishes somewhat because the agents in the
cluster are in the process of accommodating to the global lexicon. 
This means that the
languages of the different groups are in the process of
merging due to the increased language contact.

### 2015-04-27 chap6/chap6.tex
edited todo notes
fixed remaining typos

The \todo{The intro is too long} problem how a physically embodied situated agent
might refer to objects using language is extraordinarily 
difficult. If we then further want to find out how 
a group of such agents might autonomously bootstrap
a language system, the task seems almost unsurmountable. 
That is why I proposed earlier on to start by dividing
this task into its three main subtasks along the lines
of the semiotic square (\figref{square6}).
The previous chapters each focused on one of these tasks. 
\chapref{chap:5} has introduced 
perceptual mechanisms to process the raw image, segment
the scene, derive characteristics about each 
segment, and give feedback by pointing to the referent. 
\chapref{chap:4} studied categorisation mechanisms
needed for conceptualising a scene and thus for 
generating the possible meanings of a verbal
communication. \chapref{chap:5} looked at how agents can 
lexicalise meanings and build up a sufficiently shared
lexicon to engage in verbal interactions.

@@

We begin again by looking at simulations
with two agents so that we 
can clearly see the impact of multiple conceptualisations. 
The architecture of the agents has not changed, I only 
lowered the saliency treshold. 
The scenes have become a bit more complex as well. They 
now not only contain rectangles but also squares, circles, 
and triangles. This has a limited impact because the 
same sensory channels are used as before and none of them 
is really sensitive to shape properties.

@@

Game 25 illustrates this effect of 
lateral inhibition. The situation before the game is 
as depicted in \figref{triangle5}. 
Two words (with different meanings) are competing in {\bfshape  a2} to 
identify the referent: `puxazi' (meaning 
{}[\textsc{gray} 0.0–0.5], i.e. light) and `torigusu'
(meaning [\textsc{vpos} 0.0–0.5], i.e. lower).  `puxazi' has
a higher score and wins the competition. Because the game 
was successful, the score
of `puxazi' goes up. The score of `torigusu' 
does not change because it concerns another 
meaning. Two meanings for `puxazi'
are competing in {\bfshape  a1}: [\textsc{gray} 0.0–0.5] (light)
and [\textsc{vpos} 0.0–0.5] (down). [\textsc{vpos} 0.0–0.5] gets damped and 
the score of [\textsc{gray} 0.0–0.5] goes up, thus helping to 
further disambiguate `puxazi'. \clearpage
\begin{verbatim}
Game 25
  a2 is the speaker. a1 is the hearer. 
  a2 segments the context into 2 objects: 
       rectangle-0 rectangle-1 
  a2 chooses rectangle-1 as the topic 
  a2 considers as salient GRAY VPOS
  a2 categorises the topic as [VPOS 0.0–0.5] 
{}[GRAY 0.0–0.5] [GRAY 0.0–0.25]
  a2 has the words
       puxazi for [GRAY 0.0–0.5] (0.20)
       torigusu for [VPOS 0.0–0.5] (0.0)
  a2 says: `puxazi'
  a1 interprets `puxazi' as
{}[GRAY 0.0–0.5] (0.20)
{}[VPOS 0.0–0.5] (0.0)
  a1 points to rectangle-1
  a2 signals OK
\end{verbatim}
After this game, the assocation between [\textsc{gray} 0.0–0.5] 
and `puxazi' will have a score of 0.3 in both agents. 
The association between `puxazi' and [\textsc{vpos} 0.0–0.5] 
in the hearer is decreased, but because it was already 
0.0, it cannot decrease further.

>>>>

The problem how a physically embodied situated agent
might refer to objects using language is extraordinarily 
difficult. If we then further want to find out how 
a group of such agents might autonomously bootstrap
a language system, the task seems almost unsurmountable. 
That is why I proposed earlier on to start by dividing
this task into its three main subtasks along the lines
of the semiotic square (\figref{square6}).
The previous chapters each focused on one of these tasks. 
\chapref{chap:5} has introduced 
perceptual mechanisms to process the raw image, segment
the scene, derive characteristics about each 
segment, and give feedback by pointing to the referent. 
\chapref{chap:4} studied categorisation mechanisms
needed for conceptualising a scene and thus for 
generating the possible meanings of a verbal
communication. \chapref{chap:5} looked at how agents can 
lexicalise meanings and build up a sufficiently shared
lexicon to engage in verbal interactions.

@@

We begin again by looking at simulations
with two agents so that we 
can clearly see the impact of multiple conceptualisations. 
The architecture of the agents has not changed, I only 
lowered the saliency threshold. 
The scenes have become a bit more complex as well. They 
now not only contain rectangles but also squares, circles, 
and triangles. This has a limited impact because the 
same sensory channels are used as before and none of them 
is really sensitive to shape properties.

@@

Game 25 illustrates this effect of 
lateral inhibition. The situation before the game is 
as depicted in \figref{triangle5}. 
Two words (with different meanings) are competing in {\bfshape  a2} to 
identify the referent: `puxazi' (meaning 
{}[\textsc{gray} 0.0–0.5], i.e. light) and `torigusu'
(meaning [\textsc{vpos} 0.0–0.5], i.e. lower).  `puxazi' has
a higher score and wins the competition. Because the game 
was successful, the score
of `puxazi' goes up. The score of `torigusu' 
does not change because it concerns another 
meaning. Two meanings for `puxazi'
are competing in {\bfshape  a1}: [\textsc{gray} 0.0–0.5] (light)
and [\textsc{vpos} 0.0–0.5] (down). [\textsc{vpos} 0.0–0.5] gets damped and 
the score of [\textsc{gray} 0.0–0.5] goes up, thus helping to 
further disambiguate `puxazi'. \clearpage
\begin{verbatim}
Game 25
  a2 is the speaker. a1 is the hearer. 
  a2 segments the context into 2 objects: 
       rectangle-0 rectangle-1 
  a2 chooses rectangle-1 as the topic 
  a2 considers as salient GRAY VPOS
  a2 categorises the topic as [VPOS 0.0–0.5] 
{}[GRAY 0.0–0.5] [GRAY 0.0–0.25]
  a2 has the words
       puxazi for [GRAY 0.0–0.5] (0.20)
       torigusu for [VPOS 0.0–0.5] (0.0)
  a2 says: `puxazi'
  a1 interprets `puxazi' as
{}[GRAY 0.0–0.5] (0.20)
{}[VPOS 0.0–0.5] (0.0)
  a1 points to rectangle-1
  a2 signals OK
\end{verbatim}
After this game, the association between [\textsc{gray} 0.0–0.5] 
and `puxazi' will have a score of 0.3 in both agents. 
The association between `puxazi' and [\textsc{vpos} 0.0–0.5] 
in the hearer is decreased, but because it was already 
0.0, it cannot decrease further.

### 2015-04-27 chap7/chap7.tex
fixed remaining typos

These competition diagrams are an important tool to try 
and make sense of the ontological and lexical evolution
taking place in evolving groups of agents as they are
playing their language games. Typically we pick
a dominating word, for example the word `va' in 
\figref{RF-diagram}, and try to understand
why it has become dominant. 
The FM-diagram for `va' (\figref{FM-diagram}) explains
part of the story. Three stable meanings for `va' have emerged
at \todo{inserted `at' here} around 1000 games: 
[\textsc{r} 0.0–0.125], [\textsc{b} 0.3125–0.375], and [\textsc{vpos} 0.25–0.5]. 
They are all equally adequate for distinguishing the object
`va' designates, and there are no situations yet
that would have forced the disambiguation of `va'. 
In game 3000, the environment (which is continuously 
changing in this experiment) produces a scene in which
a category which was distinctive for the object designated by 
`va' is no longer distinctive. The lexicon adapts 
immediately. Around game 3000 the \textsc{vpos}-based meaning disappeares, 
and the distinction based on \textsc{red} shoots up and becomes dominant.

@@

Ambiguity\is{ambiguity} (incoherence along the FM dimension) 
is unavoidable as well for similar reasons. 
The same situation can often be conceptualised in more than 
one way and so an agent guessing the meaning of an unknown 
word or trying to make sense of a word in a particular 
context may easily derive another meaning than the one 
used by the speaker. Perceptual anomalies further aggrevate
the risk that a certain form becomes associated with 
another meaning by the hearer, as we have seen in some
grounded example games earlier on.

Different conceptualisations of the world (incoherence 
along the RM and MR dimensions) are even harder to 
avoid because every agent develops its own 
ontologies independently and without any direct 
feedback from the other agents. 
The ideal language system is not only impossible to 
attain for autonomous agents engaged in grounded
language games, it would be very 
inefficient to store and use as well because 
new words and meanings would be required for every new 
situation ever encountered. The larger the lexicon,
the harder the task of a language learner to acquire it. 
So there is a trade off between coherence and expressability. 
This is why natural languages constantly try to recruit existing 
words to keep down the repertoire of \enlargethispage{2\baselineskip} 
forms that have to be stored and hence learned.

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.80\textwidth]{chap7/figs/MF-G-025-050.pdf}}
\caption{\label{g02505.f}MF-diagram showing the
different words circulating in the population for expressing
the category [\textsc{g} 0.25–0.5]. First `xu' dominates and 
then `fepi' wins the competition after an intense struggle.}
\end{figure}

>>>>

These competition diagrams are an important tool to try 
and make sense of the ontological and lexical evolution
taking place in evolving groups of agents as they are
playing their language games. Typically we pick
a dominating word, for example the word `va' in 
\figref{RF-diagram}, and try to understand
why it has become dominant. 
The FM-diagram for `va' (\figref{FM-diagram}) explains
part of the story. Three stable meanings for `va' have emerged
at \todo{inserted `at' here} around 1000 games: 
[\textsc{r} 0.0–0.125], [\textsc{b} 0.3125–0.375], and [\textsc{vpos} 0.25–0.5]. 
They are all equally adequate for distinguishing the object
`va' designates, and there are no situations yet
that would have forced the disambiguation of `va'. 
In game 3000, the environment (which is continuously 
changing in this experiment) produces a scene in which
a category which was distinctive for the object designated by 
`va' is no longer distinctive. The lexicon adapts 
immediately. Around game 3000 the \textsc{vpos}-based meaning disappears, 
and the distinction based on \textsc{red} shoots up and becomes dominant.

@@

Ambiguity\is{ambiguity} (incoherence along the FM dimension) 
is unavoidable as well for similar reasons. 
The same situation can often be conceptualised in more than 
one way and so an agent guessing the meaning of an unknown 
word or trying to make sense of a word in a particular 
context may easily derive another meaning than the one 
used by the speaker. Perceptual anomalies further aggravate
the risk that a certain form becomes associated with 
another meaning by the hearer, as we have seen in some
grounded example games earlier on.

Different conceptualisations of the world (incoherence 
along the RM and MR dimensions) are even harder to 
avoid because every agent develops its own 
ontologies independently and without any direct 
feedback from the other agents. 
The ideal language system is not only impossible to 
attain for autonomous agents engaged in grounded
language games, it would be very 
inefficient to store and use as well because 
new words and meanings would be required for every new 
situation ever encountered. The larger the lexicon,
the harder the task of a language learner to acquire it. 
So there is a trade off between coherence and expressibility. 
This is why natural languages constantly try to recruit existing 
words to keep down the repertoire of \enlargethispage{2\baselineskip} 
forms that have to be stored and hence learned.

@@

\begin{figure}[htbp]
  \centerline{\includegraphics[width=.80\textwidth]{chap7/figs/MF-G-025-050.pdf}}
\caption{\label{g0d2505.f}MF-diagram showing the
different words circulating in the population for expressing
the category [\textsc{g} 0.25–0.5]. First `xu' dominates and 
then `fepi' wins the competition after an intense struggle.}
\end{figure}

### 2015-04-27 chap8/chap8.tex
fixed remaining typos

The installation in Antwerp was anounced as a ``Laboratory for Cognitive Robotics and Teleportation" \citep{Steels:99b}.
It featured various rooms as shown in the layout in \figref{fig:layout}. The rooms had different functions: 
\begin{enumerate} 
\item The {\itshape central room} which was visible on entering the space contained the experiment itself, i.e. the 
two cameras mounted on tripods, the computers driving them, the screen with geometric figures, and a projection of 
what went on. The activities of the agents were audible through a narration. 
\clearpage
\item A {\itshape reading room} contained background philosophical and scientific 
papers and excerpts from books about language, meaning and their origins. These readings included: \todo{The readings are referred to, but they do not follow after the colon}
\item A {\itshape user interface room} contained a workstation where visitors to the exhibition could create their own 
agents, direct them to play games on certain sites, and teach new words to their agents. 
\end{enumerate}

\begin{figure}[bp]
  \centerline{\frame{\includegraphics[width=0.9\textwidth]{chap8/figures/layout.pdf}}}
\caption{\label{fig:layout}Layout of the ``Laboratory for Cognitive Robotics and Teleporation" at the Laboratorium exhibition in Antwerp.}
\end{figure}

@@

The Paris site is really taking off now. A lexicon is beginning to 
be in place, mostly focusing on positional information (left, right, up, 
down). Because the lexicon is getting established, it is now easier for
new agents to acquire the existing lexicon and be successful. The agents have less
bushy discrimination trees and fewer but effective words. This was demosntrated
by frederic's agent (Kant) which quickly came to the top as speaker after only a
few games!

@@

The rate of communicative success for the first 200,000 games is shown in \figref{fig:allsites}. We see that the successrate is generally between 70 and 80 \%. There are occasionally crashes (e.g. around 90,000) caused by problems at a particular site (such as bad light conditions).

>>>>

The installation in Antwerp was announced as a ``Laboratory for Cognitive Robotics and Teleportation" \citep{Steels:99b}.
It featured various rooms as shown in the layout in \figref{fig:layout}. The rooms had different functions: 
\begin{enumerate} 
\item The {\itshape central room} which was visible on entering the space contained the experiment itself, i.e. the 
two cameras mounted on tripods, the computers driving them, the screen with geometric figures, and a projection of 
what went on. The activities of the agents were audible through a narration. 
\clearpage
\item A {\itshape reading room} contained background philosophical and scientific 
papers and excerpts from books about language, meaning and their origins. These readings included: \todo{The readings are referred to, but they do not follow after the colon}
\item A {\itshape user interface room} contained a workstation where visitors to the exhibition could create their own 
agents, direct them to play games on certain sites, and teach new words to their agents. 
\end{enumerate}

\begin{figure}[bp]
  \centerline{\frame{\includegraphics[width=0.9\textwidth]{chap8/figures/layout.pdf}}}
\caption{\label{fig:layout}Layout of the ``Laboratory for Cognitive Robotics and Teleportation" at the Laboratorium exhibition in Antwerp.}
\end{figure}

@@

The Paris site is really taking off now. A lexicon is beginning to 
be in place, mostly focusing on positional information (left, right, up, 
down). Because the lexicon is getting established, it is now easier for
new agents to acquire the existing lexicon and be successful. The agents have less
bushy discrimination trees and fewer but effective words. This was demonstrated
by frederic's agent (Kant) which quickly came to the top as speaker after only a
few games!

@@

The rate of communicative success for the first 200,000 games is shown in \figref{fig:allsites}. We see that the success rate is generally between 70 and 80\,\%. There are occasionally crashes (e.g. around 90,000) caused by problems at a particular site (such as bad light conditions).
